KidsAIR: Main analysis

### 2020-11-13 main_analysis_secondary_models.Rmd
analysis updates

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Started 28 Oct 2020, Updated 10 Nov 2020"
output: pdf_document
---

@@

```{r}
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(mctest)
library(tidyverse)
library(knitr)
library(kableExtra)
library(MASS)
library(faraway)
```

@@

analysis_data_winter2 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  filter(winter_id == 2)

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds")) %>% 
  dplyr::select(area, home, child_id_num, at_home, at_home_location)
```

@@

summary(itt_results)

res <- residuals(itt_results, type="deviance")
plot(predict(itt_results), res)
abline(h=0, lty=2)
qqnorm(res)
qqline(res)
halfnorm(residuals(itt_results))
```

@@

@@

```{r}
# Load results
itt_results <- read_rds(paste0(file_path, "Output/itt_results.rds"))
itt_winter1_results <- read_rds(paste0(file_path, "Output/itt_winter1_results.rds"))
#itt_winter2_results <- read_rds(paste0(file_path, "Output/itt_winter2_results.rds"))
itt_income_results <- read_rds(paste0(file_path, "Output/itt_income_results.rds"))
itt_education_results <- read_rds(paste0(file_path, "Output/itt_education_results.rds"))
itt_smoke_results <- read_rds(paste0(file_path, "Output/itt_smoke_results.rds"))
itt_burn_level_results <- read_rds(paste0(file_path, "Output/itt_burn_level_results.rds"))
itt_smoking_results <- read_rds(paste0(file_path, "Output/itt_smoking_results.rds"))
itt_windows_results <- read_rds(paste0(file_path, "Output/itt_windows_results.rds"))
itt_door_results <- read_rds(paste0(file_path, "Output/itt_door_results.rds"))
itt_sweep_results <- read_rds(paste0(file_path, "Output/itt_sweep_results.rds"))
itt_home_results <- read_rds(paste0(file_path, "Output/itt_home_results.rds"))
itt_no_age_results <- read_rds(paste0(file_path, "Output/itt_no_age_results.rds"))
itt_outlier_results <- read_rds(paste0(file_path, "Output/itt_outlier_results.rds"))

@@

# Run results through function, save, combine for plotting
itt_tidy <- results_function(itt_results, "ITT Primary")
itt_winter1_tidy <- results_function(itt_winter1_results, "ITT Winter 1")
#itt_winter2_tidy <- results_function(itt_winter2_results, "ITT Winter 2")
itt_income_tidy <- results_function(itt_income_results, "ITT + income")
itt_education_tidy <- results_function(itt_education_results, "ITT + education")
itt_smoke_tidy <- results_function(itt_smoke_results, "ITT + smoke hx")
itt_burn_level_tidy <- results_function(itt_burn_level_results, "ITT + burn level")
itt_smoking_tidy <- results_function(itt_smoking_results, "ITT + smoke act")
itt_windows_tidy <- results_function(itt_windows_results, "ITT + window act")
itt_door_tidy <- results_function(itt_door_results, "ITT + door act")
itt_sweep_tidy <- results_function(itt_sweep_results, "ITT + sweep act")
itt_home_tidy <- results_function(itt_home_results, "ITT home only")
itt_no_age_tidy <- results_function(itt_no_age_results, "ITT - age")
itt_outlier_tidy <- results_function(itt_outlier_results, "ITT outlier")

# Combine cleaned results
itt_results_combined <- rbind(itt_tidy, itt_winter1_tidy, 
                              itt_income_tidy, itt_education_tidy, 
                              itt_smoke_tidy, itt_burn_level_tidy, itt_smoking_tidy,
                              itt_windows_tidy, itt_door_tidy, itt_sweep_tidy,
                              itt_home_tidy, itt_no_age_tidy, itt_outlier_tidy)

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", 
                                   "ITT + income", "ITT + education",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT home only", "ITT - age", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  labs(y = "LRTI events per child-week \n at risk compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

@@

@@

@@

```{r}
# Load results
itt_pm_results <- read_rds(paste0(file_path, "Output/itt_pm_results.rds"))
itt_pm_winter1_results <- read_rds(paste0(file_path, "Output/itt_pm_winter1_results.rds"))
#itt_pm_winter2_results <- read_rds(paste0(file_path, "Output/itt_pm_winter2_results.rds"))
itt_pm_income_results <- read_rds(paste0(file_path, "Output/itt_pm_income_results.rds"))
itt_pm_education_results <- read_rds(paste0(file_path, "Output/itt_pm_education_results.rds"))
itt_pm_smoke_results <- read_rds(paste0(file_path, "Output/itt_pm_smoke_results.rds"))
itt_pm_burn_level_results <- read_rds(paste0(file_path, "Output/itt_pm_burn_level_results.rds"))
itt_pm_smoking_results <- read_rds(paste0(file_path, "Output/itt_pm_smoking_results.rds"))
itt_pm_windows_results <- read_rds(paste0(file_path, "Output/itt_pm_windows_results.rds"))
itt_pm_door_results <- read_rds(paste0(file_path, "Output/itt_pm_door_results.rds"))
itt_pm_sweep_results <- read_rds(paste0(file_path, "Output/itt_pm_sweep_results.rds"))
itt_pm_home_results <- read_rds(paste0(file_path, "Output/itt_pm_home_results.rds"))
itt_pm_no_age_results <- read_rds(paste0(file_path, "Output/itt_pm_no_age_results.rds"))
itt_pm_outlier_results <- read_rds(paste0(file_path, "Output/itt_pm_outlier_results.rds"))

@@

# Run results through function, save, combine for plotting
itt_pm_tidy <- results_function(itt_pm_results, "ITT Primary")
itt_pm_winter1_tidy <- results_function(itt_pm_winter1_results, "ITT Winter 1")
#itt_pm_winter2_results <- results_function(itt_pm_winter2_results, "ITT Winter 2")
itt_pm_income_tidy <- results_function(itt_pm_income_results, "ITT + income")
itt_pm_education_tidy <- results_function(itt_pm_education_results, "ITT + education")
itt_pm_smoke_tidy <- results_function(itt_pm_smoke_results, "ITT + smoke hx")
itt_pm_burn_level_tidy <- results_function(itt_pm_burn_level_results, "ITT + burn level")
itt_pm_smoking_tidy <- results_function(itt_pm_smoking_results, "ITT + smoke act")
itt_pm_windows_tidy <- results_function(itt_pm_windows_results, "ITT + window act")
itt_pm_door_tidy <- results_function(itt_pm_door_results, "ITT + door act")
itt_pm_sweep_tidy <- results_function(itt_pm_sweep_results, "ITT + sweep act")
itt_pm_home_tidy <- results_function(itt_pm_home_results, "ITT home only")
itt_pm_no_age_tidy <- results_function(itt_pm_no_age_results, "ITT - age")
itt_pm_outlier_tidy <- results_function(itt_pm_outlier_results, "ITT outlier")

# Combine cleaned results
itt_pm_results_combined <- rbind(itt_pm_tidy, itt_pm_winter1_tidy, 
                                 itt_pm_income_tidy, itt_pm_education_tidy, 
                              itt_pm_smoke_tidy, itt_pm_burn_level_tidy, itt_pm_smoking_tidy,
                              itt_pm_windows_tidy, itt_pm_door_tidy, itt_pm_sweep_tidy,
                              itt_pm_home_tidy, itt_pm_no_age_tidy, itt_pm_outlier_tidy)

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", 
                                   "ITT + income", "ITT + education",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT home only", "ITT - age", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  labs(y = "Difference in log(PM2.5) \n compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates

@@

@@

@@

```{r}
# Load results
er_results <- read_rds(paste0(file_path, "Output/er_results.rds"))
er_winter1_results <- read_rds(paste0(file_path, "Output/er_winter1_results.rds"))
#er_winter2_results <- read_rds(paste0(file_path, "Output/er_winter2_results.rds"))
er_income_results <- read_rds(paste0(file_path, "Output/er_income_results.rds"))
er_burn_level_results <- read_rds(paste0(file_path, "Output/er_burn_level_results.rds"))
er_smoking_results <- read_rds(paste0(file_path, "Output/er_smoking_results.rds"))
er_windows_results <- read_rds(paste0(file_path, "Output/er_windows_results.rds"))
er_door_results <- read_rds(paste0(file_path, "Output/er_door_results.rds"))
er_sweep_results <- read_rds(paste0(file_path, "Output/er_sweep_results.rds"))
er_home_results <- read_rds(paste0(file_path, "Output/er_home_results.rds"))
er_no_age_results <- read_rds(paste0(file_path, "Output/er_no_age_results.rds"))
er_outlier_results <- read_rds(paste0(file_path, "Output/er_outlier_results.rds"))

@@

# Run results through function, save, combine for plotting
er_tidy <- results_function(er_results, "ER Primary")
er_winter1_tidy <- results_function(er_winter1_results, "ER Winter 1")
#er_winter2_tidy <- results_function(er_winter2_results, "ER Winter 2")
er_income_tidy <- results_function(er_income_results, "ER + income")
er_burn_level_tidy <- results_function(er_burn_level_results, "ER + burn level")
er_smoking_tidy <- results_function(er_smoking_results, "ER + smoke act")
er_windows_tidy <- results_function(er_windows_results, "ER + window act")
er_door_tidy <- results_function(er_door_results, "ER + door act")
er_sweep_tidy <- results_function(er_sweep_results, "ER + sweep act")
er_home_tidy <- results_function(er_home_results, "ER home only")
er_no_age_tidy <- results_function(er_no_age_results, "ER - age")
er_outlier_tidy <- results_function(er_outlier_results, "ER outlier")

# Combine cleaned results
er_results_combined <- rbind(er_tidy, er_winter1_tidy, 
                             er_income_tidy, er_burn_level_tidy, 
                              er_smoking_tidy, er_windows_tidy, er_door_tidy,
                              er_sweep_tidy, er_home_tidy, er_no_age_tidy,
                              er_outlier_tidy)

# Plot results
er_plot_estimates <- er_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ER Primary", "ER Winter 1",
                                   "ER + income", "ER + burn level",
                                   "ER + smoke act", "ER + window act", "ER + door act",
                                   "ER + sweep act", "ER home only", "ER - age",
                                   "ER outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  labs(y = "LRTI cases per IQR \n increase in PM2.5") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "none",
          legend.text = element_text(size = 14, colour = "black")) 
er_plot_estimates

@@

>>>>

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 12 Nov 2020"
output: pdf_document
---

@@

```{r}
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(mctest)
library(tidyverse)
library(knitr)
library(kableExtra)
library(MASS)
library(faraway)
library(DHARMa)
```

@@

analysis_data_winter2 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  filter(winter_id == 2)
```

@@

summary(itt_results)
```

## Diagnostic plots
```{r}
#halfnorm(residuals(itt_results))

itt_res <- simulateResiduals(itt_results)
plot(itt_res, rank = FALSE, quantreg = TRUE)
```

The function creates two plots. To the left, a qq-uniform plot to detect deviations from overall uniformity of the residuals (calling plotQQunif), and to the right, a plot of residuals against predicted values (calling plotResiduals). Outliers are highlighted in red (for more on outliers, see testOutliers). For a correctly specified model, we would expect

a) a straight 1-1 line in the uniform qq-plot -> evidence for an overall uniform (flat) distribution of the residuals

b) uniformity of residuals in the vertical direction in the res against predictor plot

Deviations of this can be interpreted as for a linear regression. See the vignette for detailed examples.

To provide a visual aid in detecting deviations from uniformity in y-direction, the plot of the residuals against the predicted values also performs an (optional) quantile regression, which provides 0.25, 0.5 and 0.75 quantile lines across the plots. These lines should be straight, horizontal, and at y-values of 0.25, 0.5 and 0.75. Note, however, that some deviations from this are to be expected by chance, even for a perfect model, especially if the sample size is small.

@@

itt_filter_type_results <- glmer.nb(lrti_events_total ~ treatment_assigned + child_age + (1 | home:cohort:area) + 
                        filter_type +
                        offset(log_person_time_at_risk), data = analysis_data)
write_rds(itt_filter_type_results, paste0(file_path, "Output/itt_filter_type_results.rds"))

itt_filter_comp_results <- glmer.nb(lrti_events_total ~ treatment_assigned + child_age + (1 | home:cohort:area) + 
                        kw_perc_exp_cat2 + 
                        offset(log_person_time_at_risk), data = analysis_data)
write_rds(itt_filter_comp_results, paste0(file_path, "Output/itt_filter_comp_results.rds"))

@@

```{r}
# Load results
itt_results <- read_rds(paste0(file_path, "Output/itt_results.rds"))
itt_winter1_results <- read_rds(paste0(file_path, "Output/itt_winter1_results.rds"))
#itt_winter2_results <- read_rds(paste0(file_path, "Output/itt_winter2_results.rds"))
itt_income_results <- read_rds(paste0(file_path, "Output/itt_income_results.rds"))
itt_education_results <- read_rds(paste0(file_path, "Output/itt_education_results.rds"))
#itt_filter_type_results <- read_rds(paste0(file_path, "Output/itt_filter_type_results.rds"))
itt_filter_comp_results <- read_rds(paste0(file_path, "Output/itt_filter_comp_results.rds"))
itt_smoke_results <- read_rds(paste0(file_path, "Output/itt_smoke_results.rds"))
itt_burn_level_results <- read_rds(paste0(file_path, "Output/itt_burn_level_results.rds"))
itt_smoking_results <- read_rds(paste0(file_path, "Output/itt_smoking_results.rds"))
itt_windows_results <- read_rds(paste0(file_path, "Output/itt_windows_results.rds"))
itt_door_results <- read_rds(paste0(file_path, "Output/itt_door_results.rds"))
itt_sweep_results <- read_rds(paste0(file_path, "Output/itt_sweep_results.rds"))
itt_home_results <- read_rds(paste0(file_path, "Output/itt_home_results.rds"))
itt_no_age_results <- read_rds(paste0(file_path, "Output/itt_no_age_results.rds"))
itt_outlier_results <- read_rds(paste0(file_path, "Output/itt_outlier_results.rds"))

@@

# Run results through function, save, combine for plotting
itt_tidy <- results_function(itt_results, "ITT Primary")
itt_winter1_tidy <- results_function(itt_winter1_results, "ITT Winter 1")
#itt_winter2_tidy <- results_function(itt_winter2_results, "ITT Winter 2")
itt_income_tidy <- results_function(itt_income_results, "ITT + income")
itt_education_tidy <- results_function(itt_education_results, "ITT + education")
#itt_filter_type_tidy <- results_function(itt_filter_type_results, "ITT + filt type")
itt_filter_comp_tidy <- results_function(itt_filter_comp_results, "ITT + filt comp")
itt_smoke_tidy <- results_function(itt_smoke_results, "ITT + smoke hx")
itt_burn_level_tidy <- results_function(itt_burn_level_results, "ITT + burn level")
itt_smoking_tidy <- results_function(itt_smoking_results, "ITT + smoke act")
itt_windows_tidy <- results_function(itt_windows_results, "ITT + window act")
itt_door_tidy <- results_function(itt_door_results, "ITT + door act")
itt_sweep_tidy <- results_function(itt_sweep_results, "ITT + sweep act")
itt_home_tidy <- results_function(itt_home_results, "ITT home only")
itt_no_age_tidy <- results_function(itt_no_age_results, "ITT - age")
itt_outlier_tidy <- results_function(itt_outlier_results, "ITT outlier")

# Combine cleaned results
itt_results_combined <- rbind(itt_tidy, itt_winter1_tidy, 
                              itt_income_tidy, itt_education_tidy,  itt_filter_comp_tidy,
                              itt_smoke_tidy, itt_burn_level_tidy, itt_smoking_tidy,
                              itt_windows_tidy, itt_door_tidy, itt_sweep_tidy,
                              itt_home_tidy, itt_no_age_tidy, itt_outlier_tidy)

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", 
                                   "ITT + income", "ITT + education", "ITT + filt comp",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT home only", "ITT - age", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, LRTI outcome") +
  labs(y = "LRTI events per child-week \n at risk compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

ITT Winter 1 = Primary model with Winter 1 data only  
ITT + income = Primary model plus categorical income variable  
ITT + education = Primary model plus categorical education variable  
ITT + filt comp = Primary model plus variable for filter compliance  
ITT + smoke hx = Primary model plus self-reported smoking variable  
ITT + burn level = Primary model plus self-reported burn-level compared to typical  
ITT + smoke act = Primary model plus # days during sampling with smoking  
ITT + window act = Primary model plus # days during sampling with windows open  
ITT + door act = Primary model plus # days during sampling with doors open  
ITT + sweep act = Primary model plus # days during sampling with sweeping/cleaning  
ITT + home = Primary model with only home as random term  
ITT - age = Primary model without age variable  
ITT outlier = Primary model with data that fixes incidence outlier

@@

## Diagnostic plots
```{r}
plot(itt_pm_results, main = "PM ITT Primary model", 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(itt_pm_results), main = "PM ITT Primary model")
qqline(residuals(itt_pm_results))

#itt_pm_res <- simulateResiduals(itt_pm_results)
#plot(itt_pm_res, rank = TRUE, quantreg = TRUE)
```

@@

itt_pm_filter_type_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                  child_age + (1 | home:cohort:area) + 
                                  filter_type, data = analysis_data)
write_rds(itt_pm_filter_type_results, paste0(file_path, "Output/itt_pm_filter_type_results.rds"))

itt_pm_filter_comp_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                  child_age + (1 | home:cohort:area) + 
                                  kw_perc_exp_cat2, data = analysis_data)
write_rds(itt_pm_filter_comp_results, paste0(file_path, "Output/itt_pm_filter_comp_results.rds"))

@@

```{r}
# Load results
itt_pm_results <- read_rds(paste0(file_path, "Output/itt_pm_results.rds"))
itt_pm_winter1_results <- read_rds(paste0(file_path, "Output/itt_pm_winter1_results.rds"))
#itt_pm_winter2_results <- read_rds(paste0(file_path, "Output/itt_pm_winter2_results.rds"))
itt_pm_income_results <- read_rds(paste0(file_path, "Output/itt_pm_income_results.rds"))
itt_pm_education_results <- read_rds(paste0(file_path, "Output/itt_pm_education_results.rds"))
#itt_pm_filter_type_results <- read_rds(paste0(file_path, "Output/itt_pm_filter_type_results.rds"))
itt_pm_filter_comp_results <- read_rds(paste0(file_path, "Output/itt_pm_filter_comp_results.rds"))
itt_pm_smoke_results <- read_rds(paste0(file_path, "Output/itt_pm_smoke_results.rds"))
itt_pm_burn_level_results <- read_rds(paste0(file_path, "Output/itt_pm_burn_level_results.rds"))
itt_pm_smoking_results <- read_rds(paste0(file_path, "Output/itt_pm_smoking_results.rds"))
itt_pm_windows_results <- read_rds(paste0(file_path, "Output/itt_pm_windows_results.rds"))
itt_pm_door_results <- read_rds(paste0(file_path, "Output/itt_pm_door_results.rds"))
itt_pm_sweep_results <- read_rds(paste0(file_path, "Output/itt_pm_sweep_results.rds"))
itt_pm_home_results <- read_rds(paste0(file_path, "Output/itt_pm_home_results.rds"))
itt_pm_no_age_results <- read_rds(paste0(file_path, "Output/itt_pm_no_age_results.rds"))
itt_pm_outlier_results <- read_rds(paste0(file_path, "Output/itt_pm_outlier_results.rds"))

@@

# Run results through function, save, combine for plotting
itt_pm_tidy <- results_function(itt_pm_results, "ITT Primary")
itt_pm_winter1_tidy <- results_function(itt_pm_winter1_results, "ITT Winter 1")
#itt_pm_winter2_results <- results_function(itt_pm_winter2_results, "ITT Winter 2")
itt_pm_income_tidy <- results_function(itt_pm_income_results, "ITT + income")
itt_pm_education_tidy <- results_function(itt_pm_education_results, "ITT + education")
#itt_pm_filter_type_tidy <- results_function(itt_pm_filter_type_results, "ITT + filt type")
itt_pm_filter_comp_tidy <- results_function(itt_pm_filter_comp_results, "ITT + filt comp")
itt_pm_smoke_tidy <- results_function(itt_pm_smoke_results, "ITT + smoke hx")
itt_pm_burn_level_tidy <- results_function(itt_pm_burn_level_results, "ITT + burn level")
itt_pm_smoking_tidy <- results_function(itt_pm_smoking_results, "ITT + smoke act")
itt_pm_windows_tidy <- results_function(itt_pm_windows_results, "ITT + window act")
itt_pm_door_tidy <- results_function(itt_pm_door_results, "ITT + door act")
itt_pm_sweep_tidy <- results_function(itt_pm_sweep_results, "ITT + sweep act")
itt_pm_home_tidy <- results_function(itt_pm_home_results, "ITT home only")
itt_pm_no_age_tidy <- results_function(itt_pm_no_age_results, "ITT - age")
itt_pm_outlier_tidy <- results_function(itt_pm_outlier_results, "ITT outlier")

# Combine cleaned results
itt_pm_results_combined <- rbind(itt_pm_tidy, itt_pm_winter1_tidy, 
                                 itt_pm_income_tidy, itt_pm_education_tidy, itt_pm_filter_comp_tidy,
                              itt_pm_smoke_tidy, itt_pm_burn_level_tidy, itt_pm_smoking_tidy,
                              itt_pm_windows_tidy, itt_pm_door_tidy, itt_pm_sweep_tidy,
                              itt_pm_home_tidy, itt_pm_no_age_tidy, itt_pm_outlier_tidy)

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", 
                                   "ITT + income", "ITT + education", "ITT + filt comp",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT home only", "ITT - age", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, PM outcome") +
  labs(y = "Difference in log(PM2.5) \n compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates

@@

## Diagnostic plots
```{r}

er_res <- simulateResiduals(er_results)
plot(er_res, rank = TRUE, quantreg = TRUE)
```

@@

er_filter_type_results <- glmer.nb(lrti_events_total ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + filter_type +
                          (1 | home:cohort:area) + offset(log_person_time_at_risk), 
                          data = analysis_data)
write_rds(er_filter_type_results, paste0(file_path, "Output/er_filter_type_results.rds"))

er_filter_comp_results <- glmer.nb(lrti_events_total ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + kw_perc_exp_cat2 +
                          (1 | home:cohort:area) + offset(log_person_time_at_risk), 
                          data = analysis_data)
write_rds(er_filter_comp_results, paste0(file_path, "Output/er_filter_comp_results.rds"))

@@

```{r}
# Load results
er_results <- read_rds(paste0(file_path, "Output/er_results.rds"))
er_winter1_results <- read_rds(paste0(file_path, "Output/er_winter1_results.rds"))
#er_winter2_results <- read_rds(paste0(file_path, "Output/er_winter2_results.rds"))
er_income_results <- read_rds(paste0(file_path, "Output/er_income_results.rds"))
#er_filter_type_results <- read_rds(paste0(file_path, "Output/er_filter_type_results.rds"))
er_filter_comp_results <- read_rds(paste0(file_path, "Output/er_filter_comp_results.rds"))
er_burn_level_results <- read_rds(paste0(file_path, "Output/er_burn_level_results.rds"))
er_smoking_results <- read_rds(paste0(file_path, "Output/er_smoking_results.rds"))
er_windows_results <- read_rds(paste0(file_path, "Output/er_windows_results.rds"))
er_door_results <- read_rds(paste0(file_path, "Output/er_door_results.rds"))
er_sweep_results <- read_rds(paste0(file_path, "Output/er_sweep_results.rds"))
er_home_results <- read_rds(paste0(file_path, "Output/er_home_results.rds"))
er_no_age_results <- read_rds(paste0(file_path, "Output/er_no_age_results.rds"))
er_outlier_results <- read_rds(paste0(file_path, "Output/er_outlier_results.rds"))

@@

# Run results through function, save, combine for plotting
er_tidy <- results_function(er_results, "ER Primary")
er_winter1_tidy <- results_function(er_winter1_results, "ER Winter 1")
#er_winter2_tidy <- results_function(er_winter2_results, "ER Winter 2")
er_income_tidy <- results_function(er_income_results, "ER + income")
#er_filter_type_tidy <- results_function(er_filter_type_results, "ER + filt type")
er_filter_comp_tidy <- results_function(er_filter_comp_results, "ER + filt comp")
er_burn_level_tidy <- results_function(er_burn_level_results, "ER + burn level")
er_smoking_tidy <- results_function(er_smoking_results, "ER + smoke act")
er_windows_tidy <- results_function(er_windows_results, "ER + window act")
er_door_tidy <- results_function(er_door_results, "ER + door act")
er_sweep_tidy <- results_function(er_sweep_results, "ER + sweep act")
er_home_tidy <- results_function(er_home_results, "ER home only")
er_no_age_tidy <- results_function(er_no_age_results, "ER - age")
er_outlier_tidy <- results_function(er_outlier_results, "ER outlier")

# Combine cleaned results
er_results_combined <- rbind(er_tidy, er_winter1_tidy, 
                             er_income_tidy, er_filter_comp_tidy, er_burn_level_tidy, 
                              er_smoking_tidy, er_windows_tidy, er_door_tidy,
                              er_sweep_tidy, er_home_tidy, er_no_age_tidy,
                              er_outlier_tidy)

# Plot results
er_plot_estimates <- er_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ER Primary", "ER Winter 1",
                                   "ER + income", "ER + filt comp", "ER + burn level",
                                   "ER + smoke act", "ER + window act", "ER + door act",
                                   "ER + sweep act", "ER home only", "ER - age",
                                   "ER outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ER framework, LRTI outcome") +
  labs(y = "LRTI cases per IQR \n increase in PM2.5") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "none",
          legend.text = element_text(size = 14, colour = "black")) 
er_plot_estimates

@@

ER Winter 1 = Primary model with Winter 1 data only  
ER + income = Primary model using income instead of education  
ER + filt comp = Primary model plus variable for filter compliance  
ER + burn level = Primary model plus self-reported burn-level compared to typical  
ER + smoke act = Primary model plus # days during sampling with smoking  
ER + window act = Primary model plus # days during sampling with windows open  
ER + door act = Primary model plus # days during sampling with doors open  
ER + sweep act = Primary model plus # days during sampling with sweeping/cleaning  
ER + home = Primary model with only home as random term  
ER - age = Primary model without age variable  
ER outlier = Primary model with data that fixes incidence outlier
